Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-05-21 ms.tex
Add note about horizon distance
Clean up signal model

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $H_0$ and $H_{\pi/2}$, such that the coefficients depend only on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ and the basis waveforms depend only on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$,
%
\begin{eqnarray}
	H_i(\omega; \boldsymbol\theta) &=& e^{-i\omega t_\oplus}\frac{D_{1,i}}{D_\mathrm{L}}
	\left(\begin{array}{cc}
		F_{+,i}(h_i, \delta) \\
		F_{\times,i}(h_i, \delta)
	\end{array}\right)^\intercal
	\left(\begin{array}{cc}
		\cos{2\psi} & -\sin{2\psi} \\
		\sin{2\psi} & \cos{2\psi}
	\end{array}\right) \\ &\cdot&
	\left(\begin{array}{cc}
		\frac{1}{2}\left(1+\cos^2{\iota}\right) & 0 \\
		0 & \cos{\iota}
	\end{array}\right)
	\left(\begin{array}{cc}
		\cos{2\phi_c} & -\sin{2\phi_c} \\
		\sin{2\phi_c} & \cos{2\phi_c}
	\end{array}\right) \\ &\cdot&
	\left(\begin{array}{cc}
		H_0(\omega; \boldsymbol\theta_\mathrm{in}) \\
		H_{\pi/2}(\omega; \boldsymbol\theta_\mathrm{in})
	\end{array}\right).
\end{eqnarray}
%
This linear combination matches the conventions used in \cite{PhysRevD.83.084002}, and is the frequency-domain equivalent of their Equation~(2.8). The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the declination and local hour angle $h_i$ of the source, and are derived in~\cite{PhysRevD.63.042003}.

>>>>

Assuming circular orbits and no spin precession, we can write the \ac{GW} signal in each detector as a linear combination of two basis waveforms $H_0$ and $H_{\pi/2}$. For nonprecessing systems, $H_0$ and $H_{\pi/2}$ are approximately ``in quadrature'' in the same sense as the sine and cosine functions, being nearly orthogonal and out of phase by ${\pi/2}$ at all frequencies. In other words, $H_{\pi/2}(\omega) = i H_0(\omega)$ for all $\omega$. This linear combination isolates all dependence on the extrinsic parameters $\boldsymbol\theta_\mathrm{ex}$ into the coefficients and all dependence on the intrinsic parameters $\boldsymbol\theta_\mathrm{in}$ into the basis waveform,
%
\begin{eqnarray}
	\fl H_i(\omega; \boldsymbol\theta) &=& e^{-i\omega t_\oplus}\frac{D_{1,i}}{D_\mathrm{L}}
	\left(\begin{array}{cc}
		F_{+,i}(h_i, \delta) \\
		F_{\times,i}(h_i, \delta)
	\end{array}\right)^\intercal
	\left(\begin{array}{cc}
		\cos{2\psi} & -\sin{2\psi} \\
		\sin{2\psi} & \cos{2\psi}
	\end{array}\right)
	\left(\begin{array}{cc}
		\frac{1}{2}\left(1+\cos^2{\iota}\right) & 0 \\
		0 & \cos{\iota}
	\end{array}\right) \nonumber\\\fl &\cdot&
	\left(\begin{array}{cc}
		\cos{2\phi_c} & -\sin{2\phi_c} \\
		\sin{2\phi_c} & \cos{2\phi_c}
	\end{array}\right)
	\left(\begin{array}{cc}
		1 \\
		\imath
	\end{array}\right) H_0(\omega; \boldsymbol\theta_\mathrm{in}).
\end{eqnarray}
%
This linear combination matches the conventions used in \cite{PhysRevD.83.084002}, and is the frequency-domain equivalent of their Equation~(2.8). The quantities $F_{+,i}$ and $F_{\times,i}$ are the dimensionless detector antenna factors, and depend on the orientation of detector $i$ as well as the declination and local hour angle $h_i$ of the source, and are derived in~\cite{PhysRevD.63.042003}. The quantity $D_{1,i}$ is a fiducial horizon distance for detector $i$.
